Modelling Weddell Sea Food Web

### 2022-06-08 ModellingWeddellSea.Rmd
Add GAM

source("R/network_fun.r")
require(igraph)
require(multiweb)
require(tidyverse)

@@

# Read the updated database
#
wedd_df <- read_delim("Data/Wedd_mass_complete.dat",delim=" ")

>>>>

require(igraph)
require(multiweb)
require(tidyverse)
source("R/network_fun.r")

@@

# Read the updated database
#
wedd_df <- read_delim("Data/Wedd_mass_complete.dat",delim=" ",col_types="dccddc")
